Robotic Cart System

### 2020-10-27 parts/A-coppSimModeling.tex
~

%======================================================================
\chapter{Modeling in CoppeliaSim}
\label{ch: Chapter1}
%======================================================================

%----------------------------------------------------------------------
\section{Problem Statement}
%----------------------------------------------------------------------
It is important to be able to simulate a robot's behavior before using the actual robot to help find unexpected behaviors. CoppeliaSim is commercial robot simulation software with the ability to simulate a robot whose behavior is very close to the real robot. However, if the robot of interest is not already included in CoppeliaSim's library, it must be modeled. The following sections explain how to model the Runt Rover robot in CoppeliaSim.

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../finalReportMainV1"
%%% End:

>>>>

%======================================================================
\chapter{Modeling in CoppeliaSim}
\label{ch:Chapter1}
%======================================================================

%----------------------------------------------------------------------
\section{Problem Statement}
%----------------------------------------------------------------------
It is important to be able to simulate a robot's behavior before using the
actual robot to help find unexpected behaviors. CoppeliaSim is commercial robot
simulation software with the ability to simulate a robot that would operate in
exactly the way it would happen with a real robot. However, the robot of
interest is not currently included in CoppeliaSim's library that leads to
creating a model of the robot and simulating it before practical implementation.
The following sections explain how to model the Runt Rover robot in CoppeliaSim.

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../finalReport"
%%% End:
